### 2013-09-09 doc/dissertation/document/chapters/conclusion/conclusion.tex
fixed typo on cover page

\subsubsection{Physics and PDE-based Preconditioners}
Studies should be considered for physics or PDE-based preconditioners
for linear systems that produce a reduced-order model of the original
system to which the Monte Carlo method may be applied. As the Monte
Carlo method serves to construct the solution correction vector in the
MCSA method, the Monte Carlo method may be applied to a reduced-order
physics or PDE-based system that captures the essence of the original
system and still allows for acceleration of the iterative
procedure. By reducing the order of the system, we are effectively
generating a Monte Carlo problem within MCSA in which the linear
operator is either more sparse, has a better-conditioned eigenvalue
spectrum, or both. In addition, the reduced domain approximation has
shown that a purely algebraic strategy for reducing the order of the
Monte Carlo problem can result in improved overall timing performance
due to increased sparsity at the cost of iterative performance as a
result of loss of information. A more well informed strategy for order
reduction via either an intelligent simplification of the PDEs that
describe the system or a simplification of the physics involved may
prove to be a more effective strategy. In turn, this reduction of
order strategy for the Monte Carlo problem also potentially simplifies
the preconditioning strategy with less sophisticated algebraic
techniques needed for better conditioned approximations of the Monte
Carlo problem.

>>>>

\subsubsection{Physics and PDE-based Preconditioners}
Studies should be considered for physics or PDE-based preconditioners
for linear systems that produce a reduced-order model of the original
system to which the Monte Carlo method may be applied. As the Monte
Carlo method serves to construct the solution correction vector in the
MCSA method, the Monte Carlo method may be applied to a reduced-order
physics or PDE-based system instead of the original system that
captures the essence of the original system and still allows for
acceleration of the iterative procedure. By reducing the order of the
system, we are effectively generating a Monte Carlo problem within
MCSA in which the linear operator is either more sparse, has a
better-conditioned eigenvalue spectrum, or both. In addition, the
reduced domain approximation has shown that a purely algebraic
strategy for reducing the order of the Monte Carlo problem can result
in improved overall timing performance due to increased sparsity at
the cost of iterative performance as a result of loss of
information. A more well informed strategy for order reduction via
either an intelligent simplification of the PDEs that describe the
system or a simplification of the physics involved may prove to be a
more effective strategy for the acceleration step. In turn, this
reduction of order strategy for the Monte Carlo problem also
potentially simplifies the preconditioning strategy with less
sophisticated algebraic techniques needed for better conditioned
approximations of the Monte Carlo problem and therefore less
difficulty with composite operators.
